Legion: Expressing Locality and Independence with Logical Regions

### 2012-05-05 doc/sc2012/experiments.tex
Fixing the machine table
more changes

We evaluate the efficiency and scalability of Legion using
three applications on three clusters (see Figure~\ref{fig:systems}).  All three
clusters were Linux-based, and the Legion runtime was built using pthreads for
managing CPU threads, CUDA\cite{cuda} for GPUs, and GASNet\cite{GASNET07} for
inter-node communication.  The RDMA features of GASNet were used to create a 
globally addressable, but relatively slow, ``GASNet memory'' that is accessible
by all nodes.
For each application, multiple problem sizes were used, and each size problem was
run on subsets of each machine ranging from the smallest (a single CPU core or GPU)
to the largest or near-largest (except Keeneland, where we limited
runs to 32 nodes to get sufficient cluster time).
By examining performance of the same size problem over progressively larger
machines, we measure Legion's strong scaling.
By increasing the problem size as well, we also measure weak scaling.

@@

Figure~\ref{fig:ckt_speed} shows the performance of the Legion circuit simulation relative
to a hand-coded single-GPU implementation written in CUDA.  Each line shows the scaling of
a particular problem size as the number of nodes is varied.  Our results demonstrate
excellent strong scaling, with speedups of 39.0X for the small problem on 48 GPUs and 
62.5X for the larger problem size on 96 GPUs.  On a single GPU, our Legion implementation
is within 5\% of the performance of the hand-coded simulation.

@@

Figure~\ref{fig:fluid_single} compares the performance of the Legion
implementation against the PARSEC version, using a relatively small
problem (300K particles on a 15x21x15 array of cells).  Between 1 and
4 threads, the results for Sapling are nearly indistinguishable,
indicating neither the Legion runtime nor the restructuring of the
implementation to allow multi-node scaling impose any significant
overhead.
%It's possible that the use of explicit ghost cells rather than fine-grained sharing of cache lines might be a net win.  
At 8 threads and above, performance begins to vary.  Both the Legion
and PARSEC versions on Viz flatten out as they over-subscribe the 12
physical cores.  On Sapling, which has HyperThreading enabled,
deviations from linear begin sooner as the operating system's
thread placement choices begin to matter.

>>>>

We evaluate the efficiency and scalability of Legion using
three applications on three clusters (see Figure~\ref{fig:systems}).  All three
clusters were Linux-based, and the Legion runtime was built using pthreads for
managing CPU threads, CUDA\cite{CUDA} for GPUs, and GASNet\cite{GASNET07} for
inter-node communication.  The RDMA features of GASNet were used to create a 
globally addressable, but relatively slow, {\em GASNet memory} that is accessible
by all nodes.
For each application, multiple problem sizes were used, and each size problem was
run on subsets of each machine ranging from the smallest (a single CPU core or GPU)
to the largest or near-largest (except Keeneland, where we limited
runs to 32 nodes to get sufficient cluster time).
By examining performance of the same size problem over progressively larger
machines, we measure Legion's strong scaling.
By increasing the problem size as well, we also measure weak scaling.

@@

Figure~\ref{fig:ckt_speed} shows the performance of the Legion circuit simulation relative
to a hand-coded single-GPU implementation written in CUDA.  The hand-coded implementation is
able to keep the entire simulation state in fast framebuffer memory.  Each line shows the scaling of
a particular problem size as the number of nodes is varied.  Our results demonstrate
excellent strong scaling, with speedups of 39.0X for the small problem on 48 GPUs and 
62.5X for the larger problem size on 96 GPUs.  The inset in the graph shows the relative
performance for small numbers of GPUs.  On a single GPU, our Legion implementation
is within 5\% of the performance of the hand-coded simulation.

@@

Figure~\ref{fig:fluid_single} compares the performance of the Legion
implementation against the PARSEC version, using a relatively small
problem (300K particles on a 15x21x15 array of cells).  Speedups for
both the Legion and threaded PARSEC implementations are measured 
relative to PARSEC's serial version, which eliminates all locking
operations.  Between 1 and
4 threads, the PARSEC and Legion results are nearly indistinguishable,
indicating neither the Legion runtime nor the restructuring of the
implementation to allow multi-node scaling impose any significant
overhead.
%It's possible that the use of explicit ghost cells rather than fine-grained sharing of cache lines might be a net win.  
At 8 threads and above, performance begins to vary.  Both the Legion
and PARSEC versions on Viz flatten out as they over-subscribe the 12
physical cores.  On Sapling, which has HyperThreading enabled,
deviations from linear begin sooner as the operating system's
thread placement choices begin to matter.
